Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-14 Latex/journal_v1/V5/pr.tex
add sth

\begin{abstract}
Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility, Openness and reduces operational costs, allowing them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is the mixed-integer non-linear programming that is tremendously difficult.
So we broke it down into two different steps that the iterative algorithm solves it.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
The proposed method (IAPPVO) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers. Also, the simulation results attained less end-to-end delay for the proposed method than the FBDR and baseline scheme.

@@

\subsection{Power of O-RU and Fronthaul Capacity}

@@

The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
\begin{equation}\label{RM}
\begin{split}
\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
 \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
\end{split}
\end{equation}
In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
$\mathtt{M}_{u(s,i)}$ in each slice as follow.
\begin{equation}
M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
\end{equation}
\end{lemma}
Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
So the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

@@

Here, The channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.  Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent.

@@

In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
In the graph of fronthaul restriction, we have the restrictions in O-RU.
In the O-RU restriction graph, we assume that the fronhaul link is set to be 43 bits/sec/Hz (the variance of quantization noise is $10^{-12}$) , and the maximum power of each O-RU is 40 dBm. Also, the maximum power of each UE is set to be 35 dBm. Moreover, the minimum data rate for each UE in this service is 6 bits/sec/Hz. In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
The minimum data rate for each UE in this service is 6 bits/sec/Hz. 
The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
and the mean service rate is 10Mbps.
In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{cloudVsFronthaul.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UE in a Service}
  \label{fig:10}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.

>>>>

\begin{abstract}
Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility, Openness and reduces operational costs, allowing them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is the mixed-integer non-linear programming that is tremendously difficult.
So we broke it down into two different steps that the iterative algorithm solves it.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
The proposed method (IABV) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers. Also, the simulation results attained less end-to-end delay for the proposed method than the FBDR and baseline scheme.

@@

\subsection{Power of the O-RU and the Fronthaul Capacity}

@@

The left side of the equation \eqref{eqDelay}, leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
For the right side, by reformulating the equation \eqref{eqDelay}, we have a new constraint $\forall i, \forall s$ as below,
%\begin{equation}\label{RM}
%\begin{split}
%\mathcal{R}_{u(s,i)} &\geq \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
% \mathit{\langle}_{u(s,i)}&=(T^{max}_s\mu_s-3)\lambda_{u(s,i)} + \mu_s,\\
%\varpi_{u(s,i)} &= \frac{\mathfrak{M}_s \mathit{\langle}_{u(s,i)} - \alpha_s(T^{max}_s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T^{max}_s\mu_s-3)-\alpha_s T^{max}_s},\\
%\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
%\end{split}
%\end{equation}

\begin{equation}\label{RM}
\begin{split}
\mathcal{R}_{u(s,i)} &\geq \varpi_{u(s,i)}. \\
\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\\
& + \frac{3}{T^{max}_s\mu_s-\alpha_s T^{max}_s/\mathfrak{M}_s-3}\\
\end{split}
\end{equation}

In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
$\mathtt{M}_{u(s,i)}$ in each slice as follow.
\begin{equation}
M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
\end{equation}
\end{lemma}
Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
So the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

@@

Here, The channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.  Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.

@@

In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
In the graph of fronthaul restriction, we have the restrictions in O-RU.
In the O-RU restriction graph, we assume that the fronhaul link is set to be 43 bits/sec/Hz (the variance of quantization noise is $10^{-12}$) , and the maximum power of each O-RU is 40 dBm. Also, the maximum power of each UE is set to be 35 dBm. Moreover, the minimum data rate for each UE in this service is 6 bits/sec/Hz. In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
The minimum data rate for each UE in this service is 10 bits/sec/Hz. 
The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
and the mean service rate is 10Mbps.
In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{cloudVsFronthaul.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UE in a Service}
  \label{fig:10}
\end{figure}
In figure \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
After four iterations, IABV converges to the fixed value.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{iter.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of Iterations}
  \label{fig:11}
\end{figure}

%\subsection{Summary of Simulation Results}

\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
